Large-scale harmonic patterns clustering

### 2010-03-21 Paper/Paper.tex
improved by tbm, patterns for metallica mixed with vega pattern

\documentclass{article}
\usepackage{ismir2010,amsmath,cite}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algorithm,algorithmic}

@@

\subsection{EchoNest API}
We use the Echo Nest analyze API \cite{EchoNest} throughout this work.
The API gives us a chroma vector (length $12$) for every music event, 
or ``segment'', for any song we upload to their platform. 
We also get an estimate of where the beats and the bars are. Beats span over
multiple segments, and bars span over multiple beats. 
We transform the chroma vectors per segment into per beat vectors using a 
simple average. We can then stack beat vectors for a number of bars 
(usually 1 or 2). 
We get a fixed-size patch by resampling the number of chroma vectors. Typically,
there are $4$ beats per bar (Figure \ref{fig:barsize}. 
Thus an appropriate pattern size for one bar
is $12$x$4$ or $12$x$8$.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{data_sizes}
\end{center}
\caption{\small{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a code or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $10$ thousands to $2$ millions. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns.}}
\label{fig:data_sizes}
\end{figure}

@@

Looking at the most typical patterns per artist can be insightful.
To find these patters, we compare its use by one artist and divide
by its use by all artists. In Figure \ref{fig:metallica} we see 
Metallica's pattern and in Figure \ref{fig:amosvega}, Tori Amos and
Suzanne Vega's pattern. These three artists were easily identified.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.4\columnwidth]{metallica_pattern}
\end{center}
\caption{\small{Most typical pattern for Metallica.
COULD BE MIXED WITH TORI AMOS FIGURE.
}}
\label{fig:metallica}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.4\columnwidth]{toriamos_suzannevega_pattern}
\end{center}
\caption{\small{Most typical pattern for Tori Amos and Suzanne Vega.}}
\label{fig:amosvega}
\end{figure}

>>>>

\documentclass{article}
\usepackage{ismir2010,amsmath,cite}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algorithm,algorithmic}
\usepackage{subfloat,subfig}

@@

\subsection{EchoNest API}
We use the Echo Nest analyze API \cite{EchoNest} throughout this work.
The API gives us a chroma vector (length $12$) for every music event, 
or ``segment'', for any song we upload to their platform. 
We also get an estimate of where the beats and the bars are. Beats span over
multiple segments, and bars span over multiple beats. 
We transform the chroma vectors per segment into per beat vectors using a 
simple average. We can then stack beat vectors for a number of bars 
(usually 1 or 2). 
We get a fixed-size patch by resampling the number of chroma vectors. Typically,
there are $4$ beats per bar (Figure \ref{fig:barsize}). 
Thus an appropriate pattern size for one bar
is $12$x$4$ or $12$x$8$.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{data_sizes}
\end{center}
\caption{\small{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a code or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $10$ thousands to $2$ millions. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns.
OLD GRAPH WITH OLD NUMBERS
}}
\label{fig:data_sizes}
\end{figure}

@@

Looking at the most typical patterns per artist can be insightful.
To find these patters, we compare its use by one artist and divide
by its use by all artists. In Figure \ref{fig:typicalpat} we see 
Metallica's pattern, then Tori Amos and
Suzanne Vega's pattern. These three artists were easily identified.

% ignoring the two following figures
\iffalse
\begin{figure}[htb]
\begin{center}
\includegraphics[width=.4\columnwidth]{metallica_pattern}
\end{center}
\caption{\small{Most typical pattern for Metallica.
COULD BE MIXED WITH TORI AMOS FIGURE.
}}
\label{fig:metallica}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.4\columnwidth]{toriamos_suzannevega_pattern}
\end{center}
\caption{\small{Most typical pattern for Tori Amos and Suzanne Vega.}}
\label{fig:amosvega}
\end{figure}
\fi

\begin{figure}[htb]
  \centering
  \subfloat[][\small{Metallica}]{\label{fig:metallica2}\includegraphics[width=0.4\columnwidth]{metallica_pattern}}                
  \subfloat[][\small{Tori Amos / Suzanne Vega}]{\label{fig:amosvega2}\includegraphics[width=0.4\columnwidth]{toriamos_suzannevega_pattern}}
  \caption{\small{Typical patterns for different artists.}}
  \label{fig:typicalpat}
\end{figure}
